Stack Safety as a Security Property

### 2020-07-01 main.tex
Comments / polishing on section 2.

We will frequently take a prefix of the trace from an initial state up
through the first state where some condition holds on the machine state.
This can easily be implemented using \(\PUT\), and we provide special notation
for convenience.
%
Let \(f\) be a predicate on machine states. Then we define \(\mach
\hookrightarrow \machT | f\) (read ``\(\machT'\) is the prefix of
running \(\mach\) up to \(f\)''):

@@

We say that a trace of observations $\obsT_1$ is a prefix of $\obsT_2$
\leo{Benjamin suggested ``as far as an attacker is conerned in an
  e-mail, but we haven't said anything about attackers yet.}, if the
sequence of non-silent observations of $\obsT_1$ is a prefix of those
of $\obsT_2$; that is we operate up to deletion of \(\tau\)
observations, coinductively:

@@

We then define equivalence of observation traces as traces prefixing each other:
\[O_1 \simeq O_2 \triangleq O_1 \lesssim O_2 \land O_2 \lesssim O_1\]

@@

\leo{Also rephrase this.}
Second, an infinite silent trace is a prefix of (and equivalent to)
any other trace. While this might seem surprising at first, it makes
sense in a timing-insensitive context: an external observer looking
at two machine runs cannot distinguish between a machine that
steps forever or a machine that steps for a long time before producing
some output, before that time has passed.

>>>>

We will frequently take a prefix of the trace from an initial state up
through the first state where some condition holds on the machine state.
This can easily be implemented using \(\PUT\), and we provide special notation
for convenience.
%
Let \(f\) be a predicate on machine states. Then we define \(\mach
\hookrightarrow \machT | f\) (read ``\(\machT'\) is the prefix of
running \(\mach\) up to \(f\)''): \bcp{M and M' should be swapped, I think.}

@@

We say that a trace of observations $\obsT_1$ is a prefix of $\obsT_2$
\leo{Benjamin suggested ``as far as an attacker is concerned'' in an
  e-mail, but we haven't said anything about attackers yet.}\bcp{We don't
  have to talk about attackers, just external observers.}, if the
sequence of non-silent observations of $\obsT_1$ is a prefix of those
of $\obsT_2$; that is we operate up to deletion of \(\tau\)
observations, coinductively:

@@

We then define equivalence\bcp{Can we please call it something else?  An
  ``equivalence'' should always be transitive.} of observation traces as traces prefixing each other:
\[O_1 \simeq O_2 \triangleq O_1 \lesssim O_2 \land O_2 \lesssim O_1\]

@@

\leo{Also rephrase this.}
Second, an infinite silent trace is a prefix of (and equivalent to)
any other trace. While this might seem surprising at first, it makes
sense in a timing-insensitive context: an external observer looking
at two machine runs cannot (computably) distinguish between a machine that
steps forever and a machine that steps for a long time before producing
some output.
